Contribution Title\thanks{Supported by organization x.}

### 2019-10-24 paper/paper.tex
Structured the intro of Section 8

In this section, we showcase two possible use-cases of dynamic
resolvability analysis: composing separately defined DSLs
(Section~\ref{sec:evaluation-orc}), and finding ambiguities in
grammars through testing (Section~\ref{sec:evaluation-ocaml}).
%
We have implemented a tool and a small DSL for syntax definition
that generates a language definition in the style of
Section~\ref{sec:parse-time-disambiguation}, which the tool then
uses to construct a parser and do dynamic resolvability analysis.
The tool is implemented in Haskell and uses an off-the-shelf
implementation\footnote{\url{http://hackage.haskell.org/package/Earley}}
of the Earley parsing algorithm
\cite{earleyEfficientContextfreeParsing1970}.

The syntax definition DSL builds on \emph{syncons}, introduced by
Palmkvist and Broman~\cite{palmkvistCreatingDomainSpecificLanguages2019}, wherein each
production is defined separately from each other (one
\syncon{syncon} each).
%
The main difference between the DSL and the formalism in
Section~\ref{sec:parse-time-disambiguation} is that marks are
introduced as separate \syncon{forbid} declarations rather than
being inlined in productions. This allows supporting high-level
convenience constructs, e.g., specifying precedence between
previously defined operators instead of manually inserting marks,
but is also important for composability as ambiguities can be
statically resolved without changing the original definitions.
Other convenience constructs include defining prefix, infix, and
postfix operators with a given associativity.

>>>>

We have implemented a tool and a small DSL for syntax definition
(Section~\ref{sec:evaluation-syncon}) that generates a language
definition in the style of
Section~\ref{sec:parse-time-disambiguation}, which the tool then
uses to construct a parser and do dynamic resolvability analysis.
%
In this section, we showcase two possible use-cases of dynamic
resolvability analysis using this tool: composing separately
defined DSLs (Section~\ref{sec:evaluation-orc}), and finding
ambiguities in grammars through testing
(Section~\ref{sec:evaluation-ocaml}).

\subsection{A DSL for Syntax Definition}
\label{sec:evaluation-syncon}

We write our syntax definitions in a DSL building on
\emph{syncons}, introduced by Palmkvist and
Broman~\cite{palmkvistCreatingDomainSpecificLanguages2019},
wherein each production is defined separately from each other (one
\syncon{syncon} each).
%
The tool which performs the parsing is implemented in Haskell and
uses an off-the-shelf
implementation\footnote{\url{http://hackage.haskell.org/package/Earley}}
of the Earley parsing algorithm
\cite{earleyEfficientContextfreeParsing1970}.

The main difference between the DSL and the formalism in
Section~\ref{sec:parse-time-disambiguation} is that marks are
introduced as separate \syncon{forbid} declarations rather than
being inlined in productions. This allows supporting high-level
convenience constructs, e.g., specifying precedence between
previously defined operators instead of manually inserting marks,
but is also important for composability as ambiguities can be
statically resolved without changing the original definitions.
Other convenience constructs include defining prefix, infix, and
postfix operators with a given associativity.
